---
title: "HW4"
author: "Tanisha Pardasani"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Importing Packages

```{r}
library(ggplot2)
library(tidyverse)
```


## Reading Data

```{r}
# Reading in and cleaning the data
airbnb <- read.csv('AB_NYC_2019.csv', stringsAsFactors = TRUE)
airbnb$id <- NULL
airbnb$reviews_per_month <- ifelse(is.na(airbnb$reviews_per_month) == TRUE, 0,
                                   airbnb$reviews_per_month)

head(airbnb)
```

```{r}
# Structure of the data
str(airbnb)
```

```{r}
# Summary of the data
summary(airbnb)
```

```{r}
# Barplot of types of airbnbs
home_split <- ggplot(airbnb, aes(x=room_type)) + geom_bar()
home_split
```

```{r}
# Average price by room type
price_per_airbnb_type <- round(tapply(airbnb$price,
                                      airbnb$room_type, mean, na.rm=TRUE), 2)
price_per_airbnb_type
```
Entire home/apt room types are the most expensive, with an average price of $211.79 while shared rooms tend to be the least expensive, with an average price of $70.13.

```{r}
# Average number of reviews by room type
reviews_per_airbnb_type <- tapply(airbnb$reviews_per_month,
                                   airbnb$room_type, mean, na.rm=TRUE)
reviews_per_airbnb_type
```


```{r}
# Number of airbnbs by borough type
borough_split <- ggplot(data = airbnb, aes(x = neighbourhood_group)) + geom_bar()
borough_split
```

```{r}
# Number of airbnbs in the cities in the largest borough in NYC
airbnb %>%
  filter(neighbourhood_group == "Manhattan") %>%
  ggplot(aes(x=neighbourhood)) + geom_bar() +theme(axis.text.x = element_text(angle = 90))

```

```{r}
# Average price per neighborhood group
price_per_neighborhood <- round(tapply(airbnb$price,
                                      airbnb$neighbourhood_group, mean, na.rm=TRUE), 2)
price_per_neighborhood
```

Manhattan is the borough with the most expensive and the largest number of airbnbs. The neighborhoods in Manhattan with the most airbnbs are Harlem, Hell's Kitchen, East Village, the Upper West Side, and the Upper East Side.

```{r}
# Scatterplot of reviews per airbnb less than $1000
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x = number_of_reviews, y = price, alpha = .35)) + geom_point() + geom_smooth()

```

```{r}
# Scatterplot of price by minimum night
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x = minimum_nights, y = price)) + geom_point() + geom_smooth()

```
# Mapping the Top 100 Most Expensive Rentals
## Find the most expensive rentals
```{r}
abnycprice <- airbnb[order(-airbnb$price), ]
top100 <- abnycprice[1:100, ]
head(top100)
```

##Create a Map
```{r}
library(leaflet)
library(dplyr)
library(ggplot2)
leaflet(data = top100) %>%
  addTiles() %>%
  setView(-74.00, 40.71, zoom = 11) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addMarkers()
```
The map above shows that the majority of the 100 most expensive rentals are in Manhattan.

```{r}
#correlation of description length and price
description <-
airbnb %>%
summarize (name, price) %>%
mutate ( letter_count = str_length (name)) 

head(description)

avg <- ( mean ( description$letter_count))
avg

#letter counts below avg (37)
low <-
description %>%
filter ( letter_count < 38) %>%
summarize (name, price, letter_count) 
head(low)

avg_low <- ( mean ( low$letter_count))
avg_low


#letter counts below avg (37)
high <-
description %>%
filter ( letter_count > 38) %>%
summarize (name, price, letter_count) 
head(high)

avg_high <- ( mean (high$letter_count))
avg_high
```

```{r}
#plot of correlation of description length and price
description %>%
ggplot(aes(x = letter_count, y = price, alpha = .35)) + geom_point()
```

There doesn't seem to be much of a strong correlation between description length and price when looking at the plot. Most of the rentals have descriptions with 0-50 letters and the most expensive ones fall in that range. The average letter count is about 37. All the descriptions of rentals that are above 50 letters are less expensive relative to the others, but there are very few in this range.

For descriptions below the approximate average letter count of 38, the average price is about $28.58.
For descriptions above the approximate average letter count of 38, the average price is about $46.23.
These averages show that descriptions with lower letter counts tend to be cheaper. This could be because longer descriptions include more features and amenities of the airbnbs, which make them more expensive.

